---
title: "A Talk Built From Text"
subtitle: "Every slide in this deck is a demonstration of one thing"
author:
  - name: Your Name
    affiliations: Your Institution
date: today
date-format: long
---

```{r setup}
#| include: false
#
# ⚠️ ATTENTION. THESE NOTES LIVE INSIDE THE SETUP CHUNK ON PURPOSE.
#
# Quarto emits ANY content between the YAML header and the first `##` as its own
# slide, and an HTML comment counts as content. Notes written above the first
# heading therefore produce a permanently BLANK SLIDE 2, which survives every
# layout audit because an empty slide has nothing to overflow and nothing to
# misalign. `include: false` guarantees this chunk emits nothing, so notes are
# safe here. Run tools/check_blank_slides.py after every render.
#
# ==============================================================================
# WHAT THIS DECK IS
#
# A working demonstration of the components in theme/talk.scss. Every slide
# exists to show one thing, and its ::: {.notes} block says what and why.
#
# ⚠️ EVERY NUMBER IN THIS DECK IS INVENTED. figures/data/demo_results.csv is
# fabricated. Delete it before this repo becomes your deck.
#
# PICK THE COMPONENT BY WHAT THE CONTENT IS, not by habit:
#
#   ::: {.cards}     two or three PARALLEL OBJECTS of equal weight
#   ::: {.versus}    a genuine BINARY. Two columns, one hairline, no boxes
#   ::: {.keylines}  a short LIST of points. Rule-separated rows, no boxes
#   ::: {.statement} ONE SENTENCE that deserves silence around it
#
# A deck built out of one component gets BOX FATIGUE: each slide looks fine
# alone and together they read as one slide shown eight times.
#
# NEVER HARDCODE A NUMBER. Figures read a .csv. Numbers in prose come from an
# `r ...` call. See figures/R/demo_figure.R for why.
# ==============================================================================
#
# Quarto may launch R under the C locale. htmlwidgets then serializes UTF-8
# punctuation in Plotly labels as literal byte markers such as <c2><b7>. Set the
# character locale before any figure code constructs labels.
invisible(Sys.setlocale("LC_CTYPE", "en_US.UTF-8"))
source("../figures/R/demo_figure.R")
```

## What this deck is {#intro}

::: {.keylines}
::: {.lead}
**A template, not a presentation**

Every slide demonstrates one component. Its speaker notes say what the component
is for and when to reach for something else.
:::
::: {}
**It renders offline**

No webfont, no CDN, no network call at display time. Unplug the wifi and render
it.
:::
::: {}
**Two builds, and the order matters**

A folder you present from, one file you carry as insurance. Render them
backwards and the first one breaks silently.
:::
:::

::: {.notes}
`.keylines` is the default. Rule-separated rows, a bold label, no boxes. Same
information as a card row at a fraction of the chrome.

Reach for it whenever the content is a short list of points that are not
parallel objects. Most slides are this.
:::

## &nbsp; {#study1 .divider-slide background-color="#10243A"}

::: {.divider}
::: {.num}
Part one
:::
::: {.big}
A divider carries content
:::
::: {.sub}
A slide holding one word reads as a blank slide, and the room registers it as a
mistake rather than as a transition
:::
:::

::: {.notes}
A full-bleed divider is the cheapest way to give a deck structure the audience
can feel. Use one for each real section and nowhere else.

⚠️ A divider holding ONE WORD reads as a blank slide. Give it a sentence. The
`.sub` block is what turns a pause into a signpost.

Dividers and photo slides bleed past the canvas by design, so
`tools/check_fit.py` excludes them from the overflow report.
:::

## Two things that are genuinely parallel {#cards-demo}

::: {.cards .two}
::: {.card}
**Cards**

Two or three objects of EQUAL WEIGHT, each one a thing of the same kind.

Three is the maximum that stays readable from the back of a room.
:::
::: {.card .amber}
**Not cards**

A list, a contrast, or one important sentence. Each of those has its own
component and putting it in a box costs you the emphasis.
:::
:::

::: {.notes}
`.cards` is the component people overuse. It is right when the items really are
parallel objects, and wrong the rest of the time.

The `.amber` class puts the secondary colour on a card's top border. Use it on
at most one card in a row, for the one you want read second.
:::

## A binary, with no boxes around it {#versus-demo}

::: {.versus}
::: {}
**What a versus is for**

A genuine two-sided contrast. One hairline down the middle does the work that
two boxes were doing, and it does it without spending any emphasis.

The left side takes the primary colour on its label, the right side takes the
secondary. That pairing is what tells the room these are two halves of one
thing rather than two separate points.
:::
::: {}
**When not to use it**

When the two sides are not actually opposed. A versus makes a claim about the
content, and if the content does not support the claim the slide reads as
forced.

Add `.lopsided` when one side carries much more text than the other, and
measure the result rather than guessing the ratio.
:::
:::

::: {.notes}
`.versus` beats two cards for any real binary. Fewer lines on the screen, and
the hairline reads as a comparison in a way two boxes do not.
:::

## Click either card to open it {#expand-demo .card-expand}

::: {.cards .two .expandable}
::: {.card}
**Click handlers**

::: {.card-summary}
Open in any order · close again · needs a mouse or keyboard
:::

::: {.card-detail}
- **Any order, any number of times.** A fragment sequence is linear and
  one-directional. This is not.
- **It closes again**, so the original contrast is back for the next slide.
- ⚠️ **It cannot fire from a presentation clicker**, which drives reveal's next
  and prev and nothing else.
:::
:::
::: {.card .amber}
**Fragments**

::: {.card-summary}
Linear · driven by the clicker · cannot close
:::

::: {.card-detail}
- **They fire from the podium clicker**, which is the whole reason to use one.
- **They are linear.** Step one, step two, step three, forwards only.
- Anything that must happen while your hands are not on the laptop has to be a
  fragment.
:::
:::
:::

::: {.notes}
This slide demonstrates `includes/card-expand.html`. Put `.card-expand` on the
slide and `.cards.expandable` on the row.

⚠️ The trade is the whole lesson. A click handler is flexible and needs a
mouse. A fragment fires from the clicker and cannot go backwards. Choose by
where your hands will be.

⚠️ `tools/check_fit.py` measures the OPEN states of this row as well as the
closed one, because a click can push content off a slide that measured clean.
:::

## One press moves the light {#swap-demo .swap}

::: {.versus}
::: {.bg-left}
**Lit on arrival**

This column is at full strength when the slide appears. It is the premise, the
thing you say first.
:::
::: {.bg-right .fragment}
**Lit on one press**

This column starts translucent and lights when you press the clicker once. It is
the turn, the thing the slide exists to say.
:::
:::

::: {.notes}
This demonstrates `includes/spotlight-swap.html`, and it is a fragment rather
than a click target so it fires from the podium clicker.

⚠️ THE TRAP WORTH CARRYING AWAY. This is JavaScript and not CSS `:has()`.
A `:has(.fragment.visible)` rule against a class reveal adds at runtime fires on
BACKWARD arrival and not on forward clicks, and forward is the direction you
present in. Read reveal's own state from its fragment events. Do not count
clicks.
:::

## &nbsp; {#study2 .divider-slide background-color="#1F4E79"}

::: {.divider}
::: {.num}
Part two
:::
::: {.big}
Numbers, and where they come from
:::
::: {.sub}
The figure below reads a .csv. Nothing on this slide was typed by a human
:::
:::

::: {.notes}
A second divider, in the primary colour rather than the dark one, so the two
sections are distinguishable at a glance in the slide overview (`Esc`).
:::

## The treatment group pulled ahead by wave three {#figure-demo}

```{r}
demo_figure()
```

::: {.notes}
⚠️ THE NUMBERS ARE INVENTED. `figures/data/demo_results.csv` is fabricated.

THE PATTERN IS THE POINT. The slide calls a function. The function reads a
`.csv`. Some analysis script wrote the `.csv`. Nothing in the chain holds a
number a person typed, so a rerun that moves a coefficient moves this slide too.

⚠️ THE SLIDE TITLE IS THE FINDING, not the variable name. "The treatment group
pulled ahead by wave three" beats "Results" every time. The room reads the title
whether or not it reads the chart.

⚠️ A PLOTLY FIGURE IS THE PART MOST LIKELY TO BREAK ON SOMEONE ELSE'S MACHINE,
and it breaks by drawing nothing rather than by erroring. That is what
`maxScale: 1.0` in _quarto.yml protects against, and it is why
`tools/build_static_deck.py` exists.
:::

## One sentence that deserves the slide {#statement-demo}

::: {.statement .big-statement}
The component is chosen by what the content *is*, not by what the last slide
used.
:::

::: {.notes}
`.statement` is the rarest component and the most effective. Use it two or three
times in a deck, for the sentences you want the room to still have in mind at
the end.

Put nothing else on the slide. The silence around it is the whole device, and
anything else on the slide spends it.

`em` inside a statement takes the secondary colour and comes out bold rather
than italic, so one word can carry the stress.
:::

## Before you present {#checklist}

::: {.keylines .tight}
::: {.lead}
**Render both builds, in order**

The usb profile first, then the default. Backwards and the presenting deck
silently loses its whole theme.
:::
::: {}
**Run the checks**

`--fences` first, it is cheap. Then the fit check and the blank-slide check. An
unclosed `:::` once nested 44 of 54 slides and the fit check still said CLEAN.
:::
::: {}
**Then look at it**

Page through every slide. A screenshot beats a number whenever they disagree.
:::
:::

::: {.notes}
`.tight` on a layout block removes its minimum height, so it shares a slide
instead of filling one. Use it whenever a slide has a title AND a block.
:::

## &nbsp; {#thanks .divider-slide background-color="#10243A"}

::: {.divider}
::: {.big}
Thank you
:::
::: {.sub}
Questions
:::
:::

::: {.notes}
Everything after this slide is appendix. Those slides do not count toward the
progress bar and the audience never sees them unless you go there.

Press `m` for a searchable menu, or type a slide number and press Enter.
:::

{{< include appendix.qmd >}}
